\documentclass[a4paper,11pt]{article}
\usepackage{enumitem}
\usepackage{geometry}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{setspace}

% Page formatting
\geometry{left=0.5in,right=0.5in,top=0.3in,bottom=0.3in}

% Defining section formatting with blue color
\linespread{1} % Adjust the line spacing as needed
\titlespacing*{\section}{0pt}{0.5\baselineskip}{0.5\baselineskip}
\titlespacing*{\subsection}{0pt}{0.1\baselineskip}{0.2\baselineskip}
% Define the section formatting
\titleformat{\section}{\color{darkgray}\bfseries\Large}{}{0em}{}[\color{black}\titlerule]
\titleformat{\subsection}{\bfseries\large}{}{0em}{}
\titleformat{\subsubsection}{\bfseries}{}{0em}{}

% Improved custom itemize formatting
\setlist[itemize]{left=0em, itemsep=0.2em, parsep=0em, topsep=0em}

% Custom command to create space after sections
\newcommand{\sectionsep}{\vspace{0.1cm}}
\newcommand{\divider}{\vspace{0.1cm} \noindent\rule{\linewidth}{0.3pt} \vspace{0.1cm}}

% Hyperref settings to make links blue and clickable
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue,
    citecolor=blue
}

\begin{document}

% Name and contact information
\begin{center}
    {\Huge \textbf{Anoushka Chatterjee}} \\
    \vspace{5pt}
    \href{mailto:anoushka19c@gmail.com}{anoushka19c@gmail.com} $|$
    \href{tel:+918815162945}{+91 8815162945} $|$
    \href{https://www.linkedin.com/in/anoushkaacc}{LinkedIn} $|$
    \href{https://github.com/anoushkaacc}{GitHub} \\
\end{center}

\vspace{0.1cm}

% Summary section
\section*{SUMMARY}
Motivated engineering student passionate about Data Science and Artificial Intelligence. Core member of the college technical society, with a deep enthusiasm for programming. Avid reader of research papers, always eager to expand knowledge and apply it to innovative solutions.


% Education section
\section*{EDUCATION}
\subsection{{Chhattisgarh Swami Vivekananda Technical University} \small\hfill Nov 2022 - 2026 } \\
B Tech (Honours) Computer Science Engineering (Data Science) \\
CPI : 7.33

% Skills section
\section*{SKILL SET}
\begin{itemize}
    \item \textbf{Languages:} C, C++, Python, R, SQL, MATLAB
    \item \textbf{Frameworks:} NumPy, Pandas, SciKit-Learn, NLTK, Seaborn, Matplotlib
    \item \textbf{Software/Tools:} RStudio, Git, GitHub, Jupyter Lab, Tableau, VSCode, Mercurial SCM, LaTex

\end{itemize}

% Experience section
\section*{EXPERIENCE}
\subsection{{Data Science Intern, South Eastern CoalFields Limited (SECL)} \small\hfill July 2023 – Aug 2023}
\begin{itemize}
    \item Developed a predictive maintenance system using a Random Forest classifier to prevent mining equipment failures.
    \item Preprocessed datasets and performed Exploratory Data Analysis (EDA) to extract meaningful features.
    \item Automated model training, evaluation, and prediction processes using Python scripts.
    \item Achieved high accuracy, precision, and F1 score in failure prediction, reducing operational downtime.
    \item Created detailed reports and logs to track project performance and results.
\end{itemize}

% Projects section
\section*{PROJECTS}

\subsection{{Predictive Modeling for Agriculture} }
\begin{itemize}
    \item Developed a multi-class classification model to recommend optimal crops based on soil metrics like nitrogen, phosphorus, potassium, and pH levels.
    \item Preprocessed data, addressed missing values, and trained logistic regression models, achieving an F1-score of 0.2389. \href{https://github.com/anoushkaacc/Machine-Learning-fundamentals-with-Python/tree/main/Project%3A%20Predictive%20Modeling%20for%20Agriculture}{Link}
\end{itemize}

\subsection{Movie Recommendation System}
\begin{itemize}
    \item Built a Python-based recommendation system using text matching and similarity scoring to suggest up to 35 tailored movies based on user preferences. \href{https://github.com/anoushkaacc/Acmegrade-projects/tree/main/Movie%20Recommendation%20engine}{Link}
\end{itemize}

\subsection{Stroke Prediction Model in R} 
\begin{itemize}
    \item Created a stroke prediction model using Random Forest, achieving over 95\% accuracy by analyzing health data and identifying important features through logistic regression.
    \item Preprocessed data and handled missing values, improving model performance with detailed exploratory data analysis. \href{https://github.com/anoushkaacc/R-for-Data-Science}{Link} 
\end{itemize}

% Position of Responsibility section
\section*{POSITIONS OF RESPONSIBILITY}

\subsection*{Vice President, Coding Club}
\begin{itemize}
    \item Led a team of over 20 members, organizing and hosting numerous technical sessions.
    \item Trained and mentored juniors in coding and technical skills.
\end{itemize}

\subsection*{IEEE Volunteer}
\begin{itemize}
    \item Facilitated a workshop session on AR-VR technology at the IEEE International Conference on Electrical, Computer, and Communication Technologies (ICECCT 2024), showcasing expertise and enhancing the conference's technical program.
\end{itemize}

\end{document}
